---
title: "Specified Column Squared"
author: "Joshua Martin"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Specified Column Squared}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(AnalyzeSurveys)
```

##Installation Instructions

devtools::install_github("joshuamartin-3/Project_three")
library(AnalyzeSurveys)

##Introducing the squared_surveys R function.

This package was made in order to square the values in a specified column and create a new column of values. This may be useful if we want to use the squared value of a column in further calculations perhaps in statistical measurement.

##Where to get the data.

The data utilized in this package is located within the surveys.csv dataset.

This can be downloaded directly to the directory "/cloud/project/data/surveys.csv" using the code displayed below.

AnalyzeSurveys::survey_cleaner("/cloud/project/data/surveys.csv")

##Usage of the squared_surveys function.

This function takes in two parameters: 
filepath the filepath of the surveys.csv dataset
clmns which is the specified column to be manipulated and squared

AnalyzeSurveys::squared_surveys("/cloud/project/data/surveys.csv", "weight")

The dataset will return the squared values of the original column or if there is not a numerical column inputted it will provide the error message: "Input non-numeric."
