---
title: "Linear Model Comparison of Two Specified Surveys Columns"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Linear Model Comparison of Two Specified Surveys Columns}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(AnalyzeSurveys)
```

##Installion Instructions

devtools::install_github("joshua.martin-3/Project_three")
library(AnalyzeSurveys)

##Introducing the survey_lm R function.

This function was created in order to create a linear model of the relationship between two specified variable types. This function will return to the console a summary of the linear model, and saved locally will be the graphical representation of the linear model.

##Where to get the data.

The data utilized in this package is located within the surveys.csv dataset.

This can be downloaded directly to the directory "/cloud/project/data/surveys.csv" using the code displayed below.

AnalyzeSurveys::survey_cleaner("/cloud/project/data/surveys.csv")

##Sample Utilization of the survey_lm function

There are five parameters used in this function:

filepath the path to the surveys.csv dataset
predictor the variable potentially impacting the reponse variable
response the variable potentially changed by the predictor variable
x_title the user-specified x-axis title
y_title the user-specified y-axis title

AnalyzeSurveys::survey_lm("/cloud/project/data/surveys.csv", "weight", "hindfoot_length", "Weight", "Hindfoot Length")

The function will summarize the relationship and create a graphical representation of the potential effect of weight on hindfoot_length. Lastly, the function will save the graph to a file named "surveys_lm_plot.png".


