---
title: "Scatterplot Comparison of Two Surveys Columns"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Scatterplot Comparison of Two Surveys Columns}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(AnalyzeSurveys)
```


##Installion Instructions

devtools::install_github("joshua.martin-3/Project_three/AnalyzeSurveys")
library(AnalyzeSurveys)

##Introducing the survey_dotplot R function.

This function was created in order to create a custom scatterplot from the surveys.csv dataset comparing to variable types and adding user-defined axis titles. 

##Usage of the function to download the surveys dataset.

The data utilized in this package is located within the surveys.csv dataset.

This can be downloaded directly to the directory "/cloud/project/data/surveys.csv" using the code displayed below.

AnalyzeSurveys::survey_cleaner("/cloud/project/data/surveys.csv")

The code displayed above checks for the presence of the proper file in the specified filepath. If it is not there it will then download the file to the specified location. The function read_csv was used in order to save the csv file to a variable name and specify commmon NA values. Lastly, the NA values were removed from the dataset and a "clean" version of the surveys dataset was returned from the function.

##Sample usage of survey_dotplot

There are five parameters needed for this function:
filepath path of the saved surveys.csv file
x_var name of the x-axis variable
y_var name of the y-axis variable
x_title specified x-axis title
y_title specified y-axis title

AnalyzeSurveys::survey_dotplot("/cloud/project/data/surveys.csv", "weight", "hindfoot_length", "Weight", "Hindfoot Length")

The output of this function will return the scatterplot comparing the relationship between hindfoot_length and height.

