---
title: "ANOVA Analysis Summary and Scatterplot"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ANOVA Analysis Summary and Scatterplot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(AnalyzeSurveys)
```

##Installion Instructions

devtools::install_github("joshua.martin-3/Project_three")
library(AnalyzeSurveys)

##Introducing the survey_lm R function.

This function was created in order to perform an ANOVA analysis of the relationship between two specified variable types. This function will return to the console a summary of the ANOVA test, and saved locally will be the graphical representation of the linear model.

##Where to get the data.

The data utilized in this package is located within the surveys.csv dataset.

This can be downloaded directly to the directory "/cloud/project/data/surveys.csv" using the code displayed below.

AnalyzeSurveys::survey_cleaner("/cloud/project/data/surveys.csv")

##Sample Utilization of the survey_anova function

There are five parameters used in this function:

filepath the path to the surveys.csv dataset
predictor the variable potentially impacting the reponse variable
response the variable potentially changed by the predictor variable
x_title the user-specified x-axis title
y_title the user-specified y-axis title

AnalyzeSurveys::survey_anova("/cloud/project/data/surveys.csv", "weight", "hindfoot_length", "Weight", "Hindfoot Length")

The function will summarize the relationship of weight on hindfoot_length using a linear model, then the aov function was used to fit an analysis of variance model to the dataset. Next the function creates a graphical representation of the potential effect of weight on hindfoot_length as a scatterplot with the linear model trendline and r-squared. Lastly, the function will save the graph to a file named "anova_plot.png".

